Updated Criteria for the Diagnostic Procedure for Parkinson's Disease Dementia on Level I

### 2024-04-10 theart.qmd
Insert Table_comparison old and new crit

Insert Table

>>>>

```{r}
#| label: tbl-martin
#| tbl-cap: Comparison of criteia.
#| apa-note: The note below the table.

tibble::tribble(
  ~"Criteria", ~"Former", ~"New",
  "", "MMSE < 26", "MoCA < 26", 
  "Attention", "Serial 7's/months reversed", "Serial 7's",
  "Executive functions", "Lexical Fluency (S)/ Clock Drawing Test", "Lexical Fluency (K)/ Clock Drawing Test",
  "Visuo-spatial functions", "Drawing of Pentagons", "Drawing of Cube",
  "Memory", "3-Word Recall", "5-Word Recall",
  "Language", "-", "Naming of Animals",
  ) |>
  flextable::flextable() |>
  flextable::theme_apa()
```
